Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-03 paper/paper.tex
cleaned up plots displaying mutations vs IFN
The plots with IFN versus mutations were very
cluttered as they had P values, Q values, and
raw counts. Got rid of the raw counts and showed
both P and Q values on the same line in small text.

%%% begin mutations figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=\linewidth]{figures/single_cell_figures/p_mutations.pdf}
}
\caption{
Viral genetic variation partially explains the heterogeneity in viral burden and IFN induction among the infected cells for which we sequenced all expressed viral genes (\FIG{genotypes}).
{\bf (A)} 
The percent of all mRNA derived from virus, faceted by whether the cells express wildtype copies of all eight viral genes, or fail to express a wildtype copy of one or more genes (due to gene absence, amino-acid substitution, insertion, or deletion).
Cells infected by full wildtype virus exhibit less heterogeneity in viral burden as quantified by the Gini index (95\% confidence intervals are indicated).
{\bf (B)}
There is a trend for cells infected by full wildtype virus to express less IFN.
{\bf (C)}
Some specific forms of viral genetic variation are associated with IFN induction.
The top panel show the percent of IFN+ and IFN- cells that fail to express each viral gene.
The middle and bottom panels show the percent of IFN- and IFN+ cells that have a deletion or amino-acid substitution in each viral gene, conditioned on the cell expressing that gene.
Numbers above the bars give P-values (Fisher's exact test) for rejecting the hypothesis that percents are equal among IFN- and IFN+ cells. 
Absence of NS is strongly associated with IFN induction; amino-acid substitutions in PB1 or NS and deletions in HA are weakly associated with IFN induction.
\FIGSUPP[mutations]{complete_annotated} gives exact numbers and multiple-hypothesis corrections on the P-values; only the absence of NS remains significant at a false-discovery rate of 10\%.
\FIGSUPP[mutations]{all_annotated} shows that the trends are largely the same if we include infected cells with incomplete sequence information for some expressed viral genes, with the addition of a trend towards IFN induction associated with \emph{presence} of PB2 and PA. 
Insertions are not shown as a mutation type as they are extremely rare (\FIG{genotypes}).
{\bf (D)}
There is no association between IFN induction and the amount of viral mRNA in cells that express NS, but viral burden is associated with IFN induction among cells that lack NS.
Note that throughout this figure, we only consider as substitution mutations that are non-synonymous.
}
\label{fig:mutations}

\figsupp[A version of \FIG{mutations}C with cell counts and multiple-hypothesis corrections.]
{The numbers at the top show the Q-values as well as the P-values.
Only the association of absence of NS with IFN induction remains significant at a false-discovery rate of 0.1.
The fractions written in small numbers on the bars indicate the number of cells that have the indicated mutation over the total number of cells for that IFN state.
}
{\includegraphics[width=\textwidth]{figures/single_cell_figures/p_muts_ifn_complete_annot.pdf}}
\label{figsupp:complete_annotated}

\figsupp[Analysis as in \FIG{mutations}C but including infected cells with incomplete viral sequence information.]
{This plot differs from \FIG{mutations}C and \FIGSUPP[mutations]{all_annotated} in that it also includes data from cells for which some viral genes were not fully sequenced.
For incompletely sequenced cells, deletions and substitutions are included in the counts when that particular viral gene is sequenced.
The major trends in \FIG{mutations}C are also true for the larger dataset in this figure.
In addition, there is now a modest trend for infected cells that fail to express PB2 and PA \emph{not} to express IFN.
}
{\includegraphics[width=\textwidth]{figures/single_cell_figures/p_muts_ifn_all_annot.pdf}}
\label{figsupp:all_annotated}

>>>>

%%% begin mutations figure %%%
\begin{figure}
\begin{fullwidth}
{\centering
\includegraphics[width=\linewidth]{figures/single_cell_figures/p_mutations.pdf}
}
\caption{
Viral genetic variation partially explains the heterogeneity in viral burden and IFN induction among the infected cells for which we sequenced all expressed viral genes (\FIG{genotypes}).
{\bf (A)} 
The percent of all mRNA derived from virus, faceted by whether the cells express wildtype copies of all eight viral genes, or fail to express a wildtype copy of one or more genes (due to gene absence, amino-acid substitution, insertion, or deletion).
Cells infected by full wildtype virus exhibit less heterogeneity in viral burden as quantified by the Gini index (95\% confidence intervals are indicated).
{\bf (B)}
There is a trend for cells infected by full wildtype virus to express less IFN.
{\bf (C)}
Some specific forms of viral genetic variation are associated with IFN induction.
The top panel show the percent of IFN+ and IFN- cells that fail to express each viral gene.
The middle and bottom panels show the percent of IFN- and IFN+ cells that have a deletion or amino-acid substitution in each viral gene, conditioned on the cell expressing that gene.
Numbers above the bars give P-values (Fisher's exact test) and associated Q-values~\citep{storey2003statistical} for rejecting the null hypothesis that percents are equal among IFN- and IFN+ cells. 
Absence of NS is strongly associated with IFN induction, and amino-acid substitutions in PB1 or NS and deletions in HA are weakly associated with IFN induction.
Only the absence of NS remains significant at a false-discovery rate of 10\%.
\FIGSUPP[mutations]{allcells} shows that the trends remain largely the same if we also analyze infected cells with incomplete viral sequence information, with the addition of a trend towards IFN induction associated with \emph{presence} of PB2 and PA. 
Insertions are not shown as a mutation type as they are extremely rare (\FIG{genotypes}).
{\bf (D)}
There is no association between IFN induction and the amount of viral mRNA in cells that express NS, but viral burden is associated with IFN induction among cells that lack NS.
Note that throughout this figure, we only consider as substitution mutations that are non-synonymous.
}
\label{fig:mutations}

\figsupp[Analysis as in \FIG{mutations}C but including infected cells with incomplete viral sequence information.]
{This plot differs from \FIG{mutations}C in that it also includes data from cells for which some viral genes were not fully sequenced.
For incompletely sequenced cells, deletions and substitutions are included in the counts when that particular viral gene is sequenced.
The major trends in \FIG{mutations}C are also true for the larger dataset in this figure.
In addition, there is now a modest trend for infected cells that fail to express PB2 and PA \emph{not} to express IFN.
}
{\includegraphics[width=\textwidth]{figures/single_cell_figures/p_muts_ifn_all_annot.pdf}}
\label{figsupp:allcells}
